---
title: 'Tidy scraping: Foreign exchange and Nepalese economy'
author: "Deependra Dhakal"
date: "9/3/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(rvest)
require(glue)
```

## Forex data from RBB^[https://www.nrb.org.np/]

We can scrape the data from the web using rvest and allied packages. The website publishes daily exchange rate data since 1994, January 1 till date. We take today's date to grab the most recent data.

### Obtain the static links

```{r}
require(lubridate)
year_range <- seq(date("1994-01-01"), today(), by = "day") %>% 
  year() 
month_range <- seq(date("1994-01-01"), today(), by = "day") %>% 
  month() %>% 
  str_pad(width = "2", pad = "0")
day_range <- seq(date("1994-01-01"), today(), by = "day") %>% 
  day() %>% 
  str_pad(width = "2", pad = "0")

url_glued <- glue("https://www.nrb.org.np/fxmexchangerate.php?YY={year_range}&MM={month_range}&DD={day_range}&B1=Go")
```

### Prepare page downloader function

```{r}
css_selector_india <- "body > table:nth-child(2) > tbody:nth-child(1) > tr:nth-child(3) > td:nth-child(3) > table:nth-child(2) > tbody:nth-child(1) > tr:nth-child(1) > td:nth-child(1) > table:nth-child(1)"

css_path_india <- "html body table tbody tr td table tbody tr td table"

css_selector_world <- "body > table:nth-child(2) > tbody:nth-child(1) > tr:nth-child(3) > td:nth-child(3) > table:nth-child(2) > tbody:nth-child(1) > tr:nth-child(2) > td:nth-child(1) > table:nth-child(1)"

css_path_world <- "html body table tbody tr td table tbody tr td table"
```


```{r}
url_single <- url_glued[[1]] %>% 
  read_html() %>% 
  html_nodes("table") %>%
  html_table()
```


### Implement web page cleaning

### Clean data

### Visualize data

## Nepal's economic indicators 1980-2017^[https://en.wikipedia.org/wiki/Economy_of_Nepal]

### Download table

```{r}
url_wiki_np_eco <- "https://en.wikipedia.org/wiki/Economy_of_Nepal"

url_wiki_np_eco %>% 
  read_html() %>% 
  read_nodes("table") %>% 
  html_table()
```

